---
title: "Homework 5"
author: "Marisa Sobel"
date: "11/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Problem 1

Make a dataframe that contains control and experimental data from longitudinal study. Each participant is in its own file. Want in data frame: subject ID, arm, observations over time. 

#### Data import

```{r, collapse=TRUE, message=FALSE}
# dataframe containing all file names (list.files)
file_names_df = tibble(
  file_names = list.files(path = "./data/problem_1"))

# function to read csv files

read_data <- function(file_name) {
  
  read_csv(paste0("data/problem_1/", file_name))
  
}

# data frame with nested results from each file 
study_data_import = 
  file_names_df %>% 
  mutate(
    study_data = map(file_names_df$file_names, read_data))
```

#### Tidy results 

```{r, collapse=TRUE}
# unnest, transform to long format, separate file names into study arm and subject ID
study_data_tidy = 
  study_data_import %>% 
  unnest() %>% 
  gather(key = week, value = observation, week_1:week_8) %>% 
  separate(file_names, into = c("study_arm", "subject_id"), sep = "\\_") %>% 
  mutate(
    subject_id = str_replace(subject_id, "\\.csv", ""),
    subject_id = str_remove(subject_id, "^0+"), 
    week = str_replace(week, "\\week_", ""), 
    study_arm = recode(study_arm, con = "control", exp = "experimental")) 

study_data_tidy
```

#### Plot participant's observations overtime 

```{r, collapse=TRUE}
# spaghetti plot showing obs on each subject over time, comment on differences 
study_data_tidy %>% 
  ggplot(aes(x = week, y = observation, color = subject_id, group = subject_id)) + 
  geom_line() +
  facet_grid(~study_arm) +
  labs(
    title = "Observations Over 8 Weeks", 
    x = "Week", 
    y = "Observation", 
    color = "Participant") + 
  viridis::scale_color_viridis(discrete = TRUE)
```

## Problem 2

The *Washington Post* has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository [here](https://github.com/washingtonpost/data-homicides). You can read their accompanying article [here](https://www.washingtonpost.com/graphics/2018/investigations/where-murders-go-unsolved/). 

#### Data import

```{r, collapse=TRUE}
# read in csv
wp_homicide_data = 
  read_csv("./data/data-homicides-master/homicide-data.csv")
```

The dataset pulled from the *Washington Post* has **`r nrow(wp_homicide_data)`** observations across **`r ncol(wp_homicide_data)`** variables that include information about the victim (name, race, age, sex), the reported date of the homicide, and the city and location of the homicide. 

#### Number of homicies per city & Number of unsolved homicides per city

```{r, collapse=TRUE}
# create "city_state" variable
wp_homicide_data = 
  wp_homicide_data %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "))

# total number of homicides per city
homicide_tot_df = 
  wp_homicide_data %>% 
  group_by(city_state) %>% 
  summarise(homicide_tot = n()) 

homicide_tot_df

# number of unsolved homicides per city
homicide_unsolved_df = 
  wp_homicide_data %>% 
  group_by(city_state) %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  summarise(unsolved = n()) 

homicide_unsolved_df
```

#### Estimate the proportion of homicides that are unsolved in Baltimore, MD

```{r, collapse=TRUE}
# Baltimore, MD total homicide
bmd_tot = 
  wp_homicide_data %>% 
  group_by(city_state) %>% 
  summarise(total = n()) %>% 
  filter(city_state == "Baltimore, MD")

# Baltimore, MD unsolved homicide
bmd_unsolv = 
  wp_homicide_data %>% 
  group_by(city_state) %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  summarise(unsolved = n()) %>% 
  filter(city_state == "Baltimore, MD")

# join Baltimore, MD total and unsolved homicides
baltimore = inner_join(bmd_tot, bmd_unsolv, by = "city_state")

# proportion test (null = proportions in different groups are the same)
prop.test(baltimore$unsolved, baltimore$total) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  knitr::kable(digits = 3)
```

#### Estimate the proportion of homicides that are unsolved in all cities

```{r, collapse=TRUE}
# join all cities total and unsolved homicides
all_cities = inner_join(homicide_tot_df, homicide_unsolved_df, by = "city_state")

# write prop.test function
prop_test_city = function(unsolved, homicide_tot) {
  
  prop.test(unsolved, homicide_tot) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
  
}

# iterating prop.test function over all cities using map2 - 2 inputs
all_cities = 
  all_cities %>% 
  mutate(prop_city = map2(all_cities$unsolved, all_cities$homicide_tot, prop_test_city)) %>% 
  unnest()

all_cities
```

#### Plot: Estimates and CIs for each city for the proportion of homicides that are unsolved

```{r}

```

